%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Muhammad}{Umair}
\position{Full Stack Engineer{\enskip\cdotp\enskip}React Native Engineer}
\address{Rawalpindi, Pakistan}

\mobile{(+92) 309-2611414}
\email{muhammadumair523@gmail.com}
\github{sudo-umair}
\linkedin{sudo-umair}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}




%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------

% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for Full Stack Engineer Position}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Résumé}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Muhammad Umair~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a passionate Full Stack Engineer with over 4 years of experience specializing in modern web and mobile development. My expertise spans the entire development stack, from crafting responsive user interfaces with React.js and React Native to building robust backend systems with Node.js and Express. I have a proven track record of delivering high-performance applications that scale, having optimized applications to reduce load times by 30\% and significantly improve user experience metrics.

Throughout my career at Codejunkie Co., Ltd. and as a freelance developer, I've consistently demonstrated the ability to lead development teams, mentor junior developers, and implement best practices that drive project success. My experience includes refactoring legacy codebases with modern frontend practices, implementing state management solutions with Redux and Zustand, and building scalable APIs that serve thousands of users.

\lettersection{Technical Expertise}
My technical skill set encompasses the full spectrum of modern development. On the frontend, I excel with React.js, Next.js, and React Native, creating seamless cross-platform experiences. I'm proficient with modern state management tools, UI libraries like Tailwind CSS and Material-UI, and performance optimization techniques. For backend development, I specialize in Node.js, Express.js, and RESTful APIs, with experience in GraphQL and real-time features using WebSockets.

I have extensive experience with cloud services and databases, including Firebase, Supabase, MongoDB, and PostgreSQL. My DevOps knowledge includes CI/CD pipelines, cloud deployment on platforms like Vercel and Railway, and mobile app deployment to both App Store and Google Play. I'm also well-versed in testing frameworks like Jest and React Testing Library, ensuring code quality and reliability.

\lettersection{Why I'm the Right Fit}
What sets me apart is my holistic approach to software development. I don't just write code—I architect solutions that are scalable, maintainable, and user-focused. My experience leading development teams and mentoring junior developers has taught me the importance of clean code, thorough documentation, and collaborative problem-solving.

I'm particularly passionate about performance optimization and user experience. My track record includes reducing application load times by 30\%, implementing efficient caching strategies, and creating smooth, responsive interfaces that users love. I stay current with emerging technologies and best practices, ensuring that the solutions I build are not just functional today, but future-proof.

I'm excited about the opportunity to bring my full-stack expertise, leadership experience, and passion for creating exceptional user experiences to your team. I'm confident that my combination of technical skills, collaborative approach, and proven track record of delivering high-quality software solutions makes me an ideal candidate for this position.

\end{cvletter}




\end{document}
