%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mid Senior Full Stack Engineer } % Job title
    {Codejunkie. Co., Ltd.} % Organization
    {Islamabad, Pakistan} % Location
    {Mar. 2024 - Present}% Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led development of responsive, high-performance web \& mobile apps for seamless user experiences.}
        \item {Optimized UIs, reducing load times by 30\% and improving Lighthouse scores.}
        \item {Refactored legacy codebases with modern frontend practices (component-based architecture, Redux/Zustand, lazy loading).}
        \item {Enhanced app performance and responsiveness with efficient API handling, caching, and server-side optimizations using Express, Firebase, and Supabase.}
        \item {Designed and integrated RESTful APIs \& real-time features, leveraging Firebase/Supabase for authentication, database, and cloud functions.}
        \item {Mentored junior developers, conducted code reviews, and established best practices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {React Native Engineer } % Job title
    {Codejunkie. Co., Ltd.} % Organization
    {Islamabad, Pakistan} % Location
    {Feb. 2023 - Mar. 2024}% Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and optimized React Native apps for smooth, responsive user experiences.}
        \item {Built pixel-perfect UIs from Figma, ensuring consistency across mobile platforms.}
        \item {Enhanced animations with Reanimated \& Gesture Handler for better interactivity.}
        \item {Refactored components for modularity and maintainability.}
        \item {Implemented state management using Redux, Zustand, or Context API.}
        \item {Collaborated with senior devs through code reviews \& best practices.}
        \item {Fixed bugs and shipped new features to improve app stability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {Freelance} % Organization
    {Remote} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full-stack freelance developer with 4 years of experience in frontend, backend, and mobile development.}
        \item {Built and optimized web \& mobile applications, ensuring seamless performance across platforms.}
        \item {Developed scalable APIs \& backend solutions, improving efficiency and reliability.}
        \item {Implemented modern frontend architectures with React.js, React Native, Next.js, and state management tools.}
        \item {Integrated databases, authentication, and cloud services for robust app functionality.}
        \item {Collaborated with clients to deliver custom software solutions, meeting business needs effectively.}
        \item {Passionate about performance optimization, scalability, and emerging technologies.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
