%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\newpage
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {React.js, REST APIs, Dashboard Analytics, Email Automation} % Technologies
    {Engage Switch} % Project title
    {B2B Marketing Platform} % Project type
    {}
    {
      \begin{cvitems} % Description(s) of project features
        \item {Developed a responsive web platform with React.js for automated cold email outreach and lead engagement.}
        \item {Built email composition and campaign management interfaces for automated outreach functionality.}
        \item {Implemented interactive charts and dashboards to visualize campaign performance and analytics.}
        \item {Integrated REST APIs for campaign data, email tracking, and reporting capabilities.}
        \item {Optimized UI for performance and seamless user experience across devices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {React.js, Express.js, TypeScript, Tailwind CSS, Stripe} % Technologies
    {Frontline Global} % Project title
    {Full-Stack Web Application}
    {}
    {
      \begin{cvitems} % Description(s) of project features
        \item {Contributed to the development and maintenance of the Frontline Global web platform, a comprehensive travel assistance and crisis response solution for luxury, business, and adventure travelers.}
        \item {Improved overall code structure, readability, and performance across components through systematic code refactoring.}
        \item {Implemented new UI features and interactive components based on product requirements and user feedback.}
        \item {Identified and resolved UI/UX bugs across multiple devices and screen sizes to ensure consistent user experience.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {React.js, TypeScript, AI/ML Integration, LiveKit, WebSockets, Playwright} % Technologies
    {Beyond Presence} % Project title
    {Frontend AI Platform} % Project type
    {}
    {
      \begin{cvitems} % Description(s) of project features
        \item {Contributed to the frontend development of the Beyond Presence AI platform, a cutting-edge solution focused on virtual presence and AI-powered interaction.}
        \item {Helped in development of UI library for the project, creating reusable components and design system to ensure consistency across the platform.}
        \item {Built and enhanced interactive frontend components aligned with product goals and user requirements.}
        \item {Troubleshot UI issues, ensured responsiveness, and improved performance across the web application.}
        \item {Collaborated with designers to refine user experience and maintain interface consistency throughout the platform.}
        \item {Implemented comprehensive Playwright end-to-end tests to ensure application reliability and maintain code quality across the platform.}
      \end{cvitems}
    }


  \cventry
    {React Native, AI/ML Integration, Medical Imaging, Mobile Development} % Technologies
    {CureVision} % Project title
    {React Native Medical App} % Project type
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project features
        \item {Contributed to the React Native development of a cutting-edge AI-powered wound analysis system providing fully automatic and precise wound analysis in seconds.}
        \item {Implemented mobile UI components and user interface for the wound analysis application, ensuring smooth user experience on Android devices.}
        \item {Integrated AI/ML capabilities into the mobile app for automatic wound detection and 3D wound analysis functionality.}
        \item {Developed mobile features for digital wound report generation with one-click functionality for streamlined medical documentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries} 